Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
rephrase end of III.A

>>>>

The scattering transform is defined mathematically as an infinite cascade of nonlinear layers, each consisting of a wavelet transform modulus operator.
In practice, to achieve invariance to translation up to $T = 186\,\mathrm{ms}$, \ie of the order of the minimal duration between non-overlapping acoustic events, two layers of scattering transform of the audio signal $\boldsymbol{x}(t)$ suffice.
The next section describes the operations involved in temporal scattering.
